### 2021-06-07 paper/report.tex
Switch to plots showing the effect of single channels on the pessimistic scenario.

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_new_known_case_cropped}
        \caption{{\small Recorded cases: 2021 scenarios}}
        \label{fig:2021_scenarios_recorded}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_newly_infected_cropped}
        \caption{{\small Total cases: 2021 scenarios}}
        \label{fig:2021_scenarios_newly_infected}
    \end{subfigure}

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_new_known_case_cropped}
        \caption{{\small Effects of different schooling scenarios after Easter}}
        \label{fig:schooling_scenarios_easter}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_newly_infected_cropped}
        \caption{{\small TBD}}
        \label{fig:to_be_determined}
    \end{subfigure}
    \vskip3ex

>>>>

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/effect_of_channels_on_pessimistic_scenario/full_new_known_case}
        \caption{{\small Recorded cases: 2021 scenarios}}
        \label{fig:2021_scenarios_recorded}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/effect_of_channels_on_pessimistic_scenario/full_newly_infected}
        \caption{{\small Total cases: 2021 scenarios}}
        \label{fig:2021_scenarios_newly_infected}
    \end{subfigure}

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/effect_of_channels_on_pessimistic_scenario/full_new_known_case}
        \caption{{\small Effects of different schooling scenarios after Easter}}
        \label{fig:schooling_scenarios_easter}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/effect_of_channels_on_pessimistic_scenario/full_newly_infected}
        \caption{{\small TBD}}
        \label{fig:to_be_determined}
    \end{subfigure}
    \vskip3ex
